A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2024-01-09 pilot-publication/manuscript.Rmd
Incorporate patient outcomes in results

```{r, echo = FALSE}
post.training.outcomes.table <- outcome.results.tables$ci.level.0.95[["Outcomes in all patients after training, by treatment arm"]]
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
```

After training, a total of `r m30d.atls` patients in the ATLS
arm had the primary outcome, compared to `r n.m30d.ptc` (
`r p.m30d.ptc`%) patients in the PTC arm, and `r n.m30d.control` (
`r p.m30d.control`%) patients in the standard care arm. The absolute risk
difference between the ATLS and PTC arm was `r arr.atls.ptc`% units
<!--(95% CI X - X)-->, between the ATLS and standard care arms 
`r arr.atls.control`% units <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r arr.ptc.control`% units <!--(95% CI X
-X)-->. The relative risk between the ATLS and PTC arm was 
`r rr.atls.ptc` <!--(95% CI X - X)-->, between the ATLS and standard care
arms `r rr.atls.control` <!--(95% CI X - X)-->, and between the PTC
and standard care arms `r rr.ptc.control` <!--(95% CI X - X)-->.

<!--
The change from baseline for the primary outcome was X in the ATLS
arm, X in the PTC arm, and X in the standard care arm. The differences
between changes from baseline were X (95% CI X - X) between the ATLS
and PTC arms, X (95% CI X - X) between the ATLS and standard care
arms, and X (95% CI X - X) between the PTC and standard care
arms. Table X shows differences in the primary outcome between trial
arms with 75, 85, and 95% CIs. 
-->

Differences in secondary outcomes between trial arms<!-- and subgroups--> are
available as Supplementary material table \@ref(tab:secondary-outcomes).

@@

## Feasibility Outcomes
<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. Out of `r n.eligible.residents` potentially eligible
residents, `r n.residents` (`r recruitment.rate.residents`%) were
enrolled in the study. The lost to follow up rate was 
`r rate.lost.to.follow.up`, with `r n.lost.to.follow.up` out of 
`r n.patients` patients not completing 30 day follow up. Among residents
the pass rate, after two attempts, was `r rate.pass`%. The missing
data rate ranged from `r min.missing.data` to `r max.missing.data`,
with details per variable and outcome in Table 
\ref@(tab:sample-characteristics) and Supplementary material table
\@ref(tab:secondary-outcomes). <!--The differences in
distributions between observed and extracted data, for variables that
were collected through observation or interview, are shown in Table X.-->

>>>>

```{r, echo = FALSE}
## Crude 30 day mortality
m30d.atls <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "ATLS"
)
m30d.ptc <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "PTC"
)
m30d.standard.care <- inline_text(post.training.characteristics.table,
  variable = outcomes__alive_after_30_days,
  level = "Yes",
  column = "Standard care"
)

## Extract tables for absolute and relative differences
standard.care.vs.atls.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

standard.care.vs.ptc.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

atls.vs.ptc.table <- outcome.results.tables$ci.level.0.95[["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

## Absolute differences
arr.standard.care.atls <- inline_outcome_text(
  standard.care.vs.atls.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)

arr.standard.care.ptc <- inline_outcome_text(
  standard.care.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)

arr.atls.ptc <- inline_outcome_text(
  atls.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Absolute difference",
  level = "Yes"
)

## Relative differences
rr.standard.care.atls <- inline_outcome_text(
  standard.care.vs.atls.table,
  outcome = "30 day mortality",
  column = "Relative difference",
  level = "Yes"
)

rr.standard.care.ptc <- inline_outcome_text(
  standard.care.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Relative difference",
  level = "Yes"
)

rr.atls.ptc <- inline_outcome_text(
  atls.vs.ptc.table,
  outcome = "30 day mortality",
  column = "Relative difference",
  level = "Yes"
)

## Extract tables for change from baseline in 30 day mortality
absolute.change.from.baseline.table <- outcome.results.tables$ci.level.0.95[["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]
relative.change.from.baseline.table <- outcome.results.tables$ci.level.0.95[["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

## Absolute change from baseline
abs.change.standard.care <- inline_outcome_text(
  absolute.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "Standard care",
  level = "Yes"
)

abs.change.atls <- inline_outcome_text(
  absolute.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "ATLS",
  level = "Yes"
)

abs.change.ptc <- inline_outcome_text(
  absolute.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "PTC",
  level = "Yes"
)

## Relative change from baseline
rel.change.standard.care <- inline_outcome_text(
  relative.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "Standard care",
  level = "Yes"
)

rel.change.atls <- inline_outcome_text(
  relative.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "ATLS",
  level = "Yes"
)

rel.change.ptc <- inline_outcome_text(
  relative.change.from.baseline.table,
  outcome = "30 day mortality",
  column = "PTC",
  level = "Yes"
)
```

After training, a total of `r n.m30d.control` (`r p.m30d.control`%) patients in the standard care arm had the primary outcome, compared to `r m30d.atls` patients in the ATLS arm and `r m30d.ptc` patients in the PTC arm. The absolute change from baseline in the primary outcome (95% CI) in the standard care arm was `r abs.change.standard.care`% units, in the ATLS arm `r abs.change.atls`% units, and in the PTC arm `r abs.change.ptc`% units. The relative change from baseline in the primary outcome (95% CI) in the standard care arm was `r rel.change.standard.care`, in the ATLS arm `r rel.change.atls`, and in the PTC arm `r rel.change.ptc`.

The absolute risk difference between the standard care and ATLS arms (95% CI) was `r arr.standard.care.atls`% units, between the standard care and PTC arms (95% CI) `r arr.standard.care.ptc`% units, and between the ATLS and PTC arms (95% CI) `r arr.atls.ptc`% units. The relative risk in the standard care arm compared with the ATLS arm (95% CI) was `r rr.standard.care.atls`, in the standard care arm compared with the PTC arm (95% CI) `r rr.standard.care.ptc`, and in the ATLS arm compared with the PTC arm (95% CI) the relative risk was `r rr.atls.ptc`. The absolute and relative differences in changes from baseline comparing the three arms are shown in Supplementary materials, along with data on all other outcomes.

@@

## Feasibility Outcomes
<!--Out of X potentially eligible patients, X (X%) patients were enrolled
in the study-->. Out of `r n.eligible.residents` potentially eligible residents, `r n.residents` (`r recruitment.rate.residents`%) participated in the study. The lost to follow up rate was `r rate.lost.to.follow.up`, with `r n.lost.to.follow.up` out of `r n.patients` patients not completing 30 day follow up. Among residents the pass rate, after two attempts, was `r rate.pass`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`, with details per variable and outcome in Table  \ref@(tab:sample-characteristics) and Supplementary material table
\@ref(tab:secondary-outcomes). <!--The differences in distributions between observed and extracted data, for variables that were collected through observation or interview, are shown in Table X.-->
